Stack Safety as a Security Property

### 2020-06-25 main.tex
CP - conf

In this section we will describe stack safety as a formal
property.
\leo{Should call maps and returns go here or in preliminaries?}

\paragraph*{Program Structure}

@@

\paragraph*{State Returns}

@@

\leo{How do we initialize the first policy state based on a call map? It's not
  part of the policy. Do we parameterize policies?}

\paragraph*{Stack safety}

  A stack safety property is a property of a transition system, a policy, a
  call map and a code map, that is decomposed into an integrity property and a
  confidentiality property.

    \[\begin{split}
      \textit{stack safety} \triangleq \textit{stack integrity} \land
      \textit{stack confidentiality} \\
    \end{split}\]

  \leo{TODO: Rephrase from introduction} Informally, {\it Stack
  integrity} states that if a function call returns, the caller's
  private stack data will be identical to what it was before the
  call. {\it Stack confidentiality} states that data outside a callee's
  stack frame is secret, and do not interfere with its observable
  behavior or with the machine state at return.

@@

  \leo{What about instructions? Shouldn't they be LC/HI?}
  \sna{Now we are dealing with this!}

  When \(\mach_c\) is a call state \(\callmap(\mach(\PCname)) = n\) for some
  \(n\) and \(\mach_c \stepstoobs{\obs} \mach_e\), we can construct a contour
  based on the bounds of the callee's stack frame. Instructions are low
  confidentiality if they belong to the callee and high confidentiality
  otherwise; regardless they are always high integrity.

  The private state of the callee is the entire area of the memory from stack
  base to stack pointer, with the exception of the $n$ locations
  corresponding to the arguments of a call. Private components are marked
  high confidentiality and high integrity: the callee should be able to
  neither read, nor write them.

  Everything above the stack pointer at the point of the call is
  ``uninitialized'' memory that can be written into but should not be
  read. To protect the callee itself from such reads, these components
  are marked high confidentiality and low integrity.

  Registers and the frame of arguments to the callee are free for the
  callee to use, and are therefore tagged with low integrity and low
  confidentiality.

@@

@@

  Confidentiality is in the style of non-interference, comparing the behavior
  of a program with an arbitrary variant that preserves low confidentiality data
  but may have any configuration of high confidentiality data. We define two
  machine states as variants given a contour if they agree on low
  confidentiality data:
  \[\mach \approx_\contour \mach' \triangleq \forall \component .
    \contour(\component) = \LOWSEC \rightarrow \mach(\component) =
    \mach'(\component)\]

  A system satisfies eager stack confidentiality with respect to a call map
  \(\callmap\) and code map \(\codemap\) if for any initial mpstate
  \(\mpstatename = \mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\) and each
  adjacent pair of a call state \(\mach_c\) and state \(\mach_e\) with policy
  state \(\pol_e\) in the induced trace from \(\mpstatename\), where
  \(\callmap(\mach_c(\PCname)) = n\) and \(\codemap(\mach_e(\PCname)) =
  \funid\), one of two cases holds on the induced traces from
  \(\mpstate{\mach_e}{\pol_e}\) and any variation \(\mach_e'\) with respect
  to the contour \(\mathit{Cof}(\mach_c,\funid,n)\).

  If the trace from the call reaches a return -- \(\mpstate{\mach_e}{\pol_e}
  \hookrightarrow_P \MPT | \ret{\mach_c}\) -- then the trace from the variant
  \(\mach_e'\) reaches a return -- \(\mach_e' \hookrightarrow \machT |
  \ret{\mach_c}\). Let \(\mach_r\) and \(\mach_r'\) be the final states of
  \(\pi_m(\MPT)\) and \(\machT\), respectively. Until their final states,
  \(\MPT\) and \(\machT\) must be observationally equivalent, \(\pi_o(\MPT)
  \cdot \tau \eqsim \pi_o(\machT) \cdot \tau\). For any component
  \(\component\) where \(\mach_e(\component) \not = \mach_r(\component)\) or
  \(\mach_e'(\component) \not = \mach_r'(\component)\),
  \(\mach_r\) agrees with \(\mach_r'\) on \(\component\).

  If the trace from the call never reaches a return, neither does the
  trace from the variant. Then if \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P
  \MPT\) and \(\mach_c' \hookrightarrow \machT\), \(\MPT \sim_P \machT\).

>>>>

In this section we will describe stack safety as a formal property. We
begin with our model of knowledge about the program structure\leo{I
  hate this}, and then dive in to local state encapsulation and
well-bracketed control flow.

\subsection{Program Structre}

@@

\paragraph*{What is a return?}

@@

\subsection{Local State Encapsulation}

The first part of stack safety is {\em local state encapsulation}.
Informally, it captures the notion that a caller's data is
protected from a callee's actions. We formalize this notion
as a security property with a confidentiality and an integrity
component, where the former protects the caller's data from being
read and the latter from being written.

@@

When \(\mach_c\) is a call state \(\callmap(\mach(\PCname)) = n\) for
some \(n\) and \(\mach_c \stepstoobs{\obs} \mach_e\), we can construct
a contour based on the bounds of the callee's stack frame.
%
The private state of the callee is the entire area of the memory from
stack base to stack pointer, with the exception of the $n$ locations
corresponding to the arguments of a call. Private components are
marked high confidentiality and high integrity: the callee should be
able to neither read, nor write them.
%  
Everything above the stack pointer at the point of the call is
``uninitialized'' memory that can be written into but should not be
read. To protect the callee itself from such reads, these components
are marked high confidentiality and low integrity.
%
Special care is needed for the code memory corresponding to the
callee: they are marked low confidentiality if they belong to the
callee and high confidentiality otherwise; regardless they are always
high integrity.\leo{That would mean we scramble some instructions, I
  guess that makes sense.}
%
Finally, registers and the frame of arguments to the callee are free
for the callee to use, and are therefore tagged with low integrity and
low confidentiality.

@@

\paragraph*{Stack Confidentiality}

Confidentiality is a noninterference-style property, comparing the
behavior of a program with an arbitrary variant that preserves low
confidentiality data but may have any configuration of high
confidentiality data.

\definition{Variations}

We say two machine states $\mach$ and $\mach'$ are {\em variations} of one
another given a contour $\contour$ if they agree on low
confidentiality data:
  \[\mach \approx_\contour \mach' \triangleq \forall \component .
    \contour(\component) = \LOWSEC \rightarrow \mach(\component) =
    \mach'(\component)\]

A system satisfies eager {\em stack confidentiality} with respect to a
call map \(\callmap\) and a code map \(\codemap\) if for any initial
mpstate $\mpstate{\mach_0}{\pol_0}$
%\(\mpstatename = \mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\)
and each adjacent pair of a call state \(\mach_c\) and state
\(\mach_e\) with policy state \(\pol_e\) in the induced trace from
\(\mpstatename\), where \(\callmap(\mach_c(\PCname)) = n\) and
\(\codemap(\mach_e(\PCname)) = \funid\), one of two cases holds on the
induced traces from \(\mpstate{\mach_e}{\pol_e}\) and any variation
\(\mach_e'\) with respect to the contour
\(\mathit{Cof}(\mach_c,\funid,n)\):

\begin{itemize}
\item
If the trace from the call reaches a return -- \(\mpstate{\mach_e}{\pol_e}
  \hookrightarrow_P \MPT | \ret{\mach_c}\) -- then the trace from the variant
  \(\mach_e'\) reaches a return -- \(\mach_e' \hookrightarrow \machT |
  \ret{\mach_c}\). Let \(\mach_r\) and \(\mach_r'\) be the final states of
  \(\pi_m(\MPT)\) and \(\machT\), respectively. Until their final states,
  \(\MPT\) and \(\machT\) must be observationally equivalent, \(\pi_o(\MPT)
  \cdot \tau \eqsim \pi_o(\machT) \cdot \tau\). For any component
  \(\component\) where \(\mach_e(\component) \not = \mach_r(\component)\) or
  \(\mach_e'(\component) \not = \mach_r'(\component)\),
  \(\mach_r\) agrees with \(\mach_r'\) on \(\component\).
\item
  If the trace from the call never reaches a return, neither does the
  trace from the variant. Then if \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P
  \MPT\) and \(\mach_c' \hookrightarrow \machT\), \(\MPT \sim_P \machT\).
\end{itemize}

@@
